Sensitivity Analysis

### 2023-09-14 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
14.09

	The sensitivity equations were solved simultaneously with the original process model. The focus of this work is to investigate the influence of inlet temperature, pressure and mass flow-rate on the state-space as wall as on the extraction yield. The process model and parameters have been discussed in {\color{red}article 1}. The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar. The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$ and 250 bar and 0.4 l/min.

@@

	The increase of the mass-flow rate affects the whole system simultaneously in the spatial direction. The change in mass flow-rate makes the fluid moves faster, but its thermodynamic state is not affected. As the result, Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.

@@

    Similarly, the energy in the system (defined as $\rho \times h$) is not affected as presented on Figure \ref{fig:Sensitivty_F_H}. As pressure and temperature are not affected by the increase in the mass flow-rate, the fluid density $\rho$ and enthalpy $h$ are insensitive to flow-rate change.

>>>>

	The sensitivity equations were solved simultaneously with the original process model. The focus of this work is to investigate the influence of inlet temperature, pressure and mass flow-rate on the state-space as wall as on the extraction yield. The process model and parameters have been discussed in {\color{red}article 1}. The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar. The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$, 250 bar, 0.4 l/min and the simulation was performed with the time step of 0.01 [min].

@@

	The increase of the mass-flow rate affects the whole system simultaneously in the spatial direction. The change in mass flow-rate makes the fluid moves faster, but its thermodynamic state is not affected. \todo{Change the description} As the result, Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.

@@

    Similarly, the energy in the system (defined as $\rho \times h$) is not affected as presented on Figure \ref{fig:Sensitivty_F_H}. As pressure and temperature are not affected by the increase in the mass flow-rate, the fluid density $\rho$ and enthalpy $h$ are insensitive to flow-rate change. \todo{Change the description}
